---
title: "Creating Violin Figures"
author: "Henrik Grenersen"
date: "2024-11-27"
output: html_document
---

```{r setup, include=FALSE}
setwd("C:\\Users\\47980\\OneDrive - NTNU\\Documents\\FYSMAT\\Femte\\Fall\\Prosjektoppgave\\Code")

source("C:/Users/47980/OneDrive - NTNU/Documents/FYSMAT/Femte/Fall/Prosjektoppgave/Code/Scripts/12) Combining CV estimates and IWs.R")

source("C:/Users/47980/OneDrive - NTNU/Documents/FYSMAT/Femte/Fall/Prosjektoppgave/Code/Scripts/17) CV simulations for all noisy data.R")

source("Scripts\\Scoring Rules.R")

library(ggplot2)

library(kableExtra)
```

# Creating a function that loads data 

```{r}
loadData_from_cluster <- function(beta, method="LOOCV", nFolds = 0, prefix="Representative"){
  # Function to load a single CV result from the cluster, stored
  # in folder VsCode\\Data\\Beta=beta\\CV
  prefix <- prefix <- paste0("..\\VsCode\\Data\\Beta=", beta, "\\CV\\")
  if(method=="LOOCV"){
    preds <- readRDS(paste0(prefix, "LOOCV\\Final Preds.rds"))
    pred_var <- readRDS(paste0(prefix, "LOOCV\\Final Pred vars.rds"))
    return(list(preds=preds, pred_var=pred_var))
  }
  if(method=="K"){
    prefix <- paste0(prefix, nFolds, "-fold\\")
    
    preds <- readRDS(paste0(prefix, "Final Preds.rds"))
    pred_var <- readRDS(paste0(prefix, "Final Pred vars.rds"))
    foldIds <- readRDS(paste0(prefix, "Final Fold indices.rds"))
    
    return(list(preds=preds, pred_var=pred_var, foldIds=foldIds))
  }
  
  if(method=="BLOCK"){
    prefix <- paste0(prefix, nFolds, "-block\\")
    
    preds <- readRDS(paste0(prefix, "Final Preds.rds"))
    pred_var <- readRDS(paste0(prefix, "Final Pred vars.rds"))
    foldIds <- readRDS(paste0(prefix, "Final Fold indices.rds"))
    
    return(list(preds=preds, pred_var=pred_var, foldIds=foldIds))
  }
  
}

load_all_from_cluster <- function(beta){
  # Loads all the CV results and stores them in a list
  
  res_list <- list()
  
  # Loading the datasets used
  
  prefix <-  paste0("..\\VsCode\\Data\\Beta=", beta, "\\Data\\")
   
  res_list$data <- readRDS(paste0(prefix, "Datasets.rds"))
  
  # CV methods
  
  res_list$LOOCV <- loadData_from_cluster(beta)
  
  res_list$fold_9 <- loadData_from_cluster(beta, "K", nFolds=9)
  
  res_list$fold_25 <- loadData_from_cluster(beta, "K", nFolds=25)
  
  res_list$block_9 <- loadData_from_cluster(beta, "BLOCK", nFolds=9)
  
  res_list$block_25 <- loadData_from_cluster(beta, "BLOCK", nFolds=25)
  
  # IWs
  
  prefix <-  paste0("..\\VsCode\\Data\\Beta=", beta, "\\IWs\\")
  
  res_list$KMM <- readRDS(paste0(prefix, "Tuned KMM IWs.rds"))
  
  res_list$KLIEP <- readRDS(paste0(prefix, "KLIEP IWs.rds"))
  
  # Note that the Voronoi weights were stored as areas, not
  # weights, they will be normalized with the true weights
  
  res_list$Vor <- readRDS(paste0(prefix, "Voronoi IWs.rds"))
  
  prefix <- paste0("..\\VsCode\\Data\\Beta=", beta, "\\True\\")
  
  res_list$true_IWs <- readRDS(paste0(prefix, "Importance weights.rds"))
  
  for(k in 1:ncol(res_list$Vor)){
    res_list$Vor[, k] <- res_list$Vor[, k]/mean(res_list$Vor[, k])
    
    res_list$true_IWs[, k] <- res_list$true_IWs[,k]/mean(res_list$true_IWs[, k])
  }
  
  # The ECRPS
  
  res_list$ECRPS <- readRDS(paste0(prefix, "ECRPS.rds"))
  
  # Median KMM
  prefix <-  paste0("..\\VsCode\\Data\\Beta=", beta, "\\IWs\\")
  res_list$KMM_med <- readRDS(paste0(prefix, "Median KMM IWs.rds"))
  
  return(res_list)
}

lok <- load_all_from_cluster(0.5)

plotId <- 1

ggplot(lok$data[[plotId]], aes(x=x, y=y, color=lok$block_25$pred_var[, plotId]))+
  geom_point()+
  coord_equal()
```

The result from the above function is a list that for all CV methods contain predictions and prediction variances for a given beta. It also contains the data, the importance weights and also the ECRPS. 

# Plotting function comparing IWs

```{r}
df  <- load_all_from_cluster(0)

compare_IWs_violin <- function(res_list, beta=0){
  
  MSEs <- c(mean((res_list$true_IWs-res_list$KMM)^2),
            mean((res_list$true_IWs-res_list$KMM_med)^2),
            mean((res_list$true_IWs-res_list$KLIEP)^2),
            mean((res_list$true_IWs-res_list$Vor)^2))
  
  maxes <- c(max(-(res_list$true_IWs-res_list$KMM)),
            max(-(res_list$true_IWs-res_list$KMM_med)),
            max(-(res_list$true_IWs-res_list$KLIEP)),
            max(-(res_list$true_IWs-res_list$Vor)))

  
  annotations <- data.frame(
  x = c("Tuned KMM", "Median KMM", "KLIEP", "Voronoi"),
  mse = MSEs,
  max = maxes
)
  
  plot_df <- data.frame(KMM=c(res_list$KMM),
                   KMM_med =c(res_list$KMM_med),
                   KLIEP = c(res_list$KLIEP), 
                   Vor = c(res_list$Vor),
                   true_IWs = c(res_list$true_IWs))
  
  fig<- ggplot(plot_df)+
    geom_violin(aes(x="Tuned KMM", y=KMM-true_IWs))+
    geom_violin(aes(x="Median KMM", y=KMM_med-true_IWs))+
    geom_violin(aes(x="KLIEP", y=KLIEP-true_IWs))+
    geom_violin(aes(x="Voronoi", y=Vor-true_IWs))+
    geom_text(data = annotations, aes(x = x, y = 10, label = paste0( formatC(mse, format = "e", digits = 2))), 
            vjust = 0, size = 3)+
    labs(x="", y="Bias for estimated IWs")+
    #ggtitle(paste0("Estimated importance weights for beta=", beta))+
    ylim(-20,20)
  fig
}
```


# Bootstrapping

```{r}
library(boot)
boot_statistic <- function(og_data, bootstrap_indices, ECRPS_vals){
  CV_estimates_boot <- og_data[bootstrap_indices]
  ECRPS_boot <- ECRPS_vals[bootstrap_indices]
  mean((CV_estimates_boot-ECRPS_boot)^2)
}

res_list <- load_all_from_cluster(0)

CV_estimates <- aggregate_CV(res_list$block_9, Datasets = res_list$data)

boot_obj <- boot(data=CV_estimates,
                 statistic = boot_statistic,
                 R= 10000,
                 ECRPS_vals = res_list$ECRPS)

plot(boot_obj)

int <- boot.ci(boot_obj)

int$normal
```

# Creating latex tables:

## LOOCV
```{r, asis=TRUE}
betas <- c(0, 0.5, 1, 1.5, 2)

IW_types <- c("None", "KMM", "KLIEP", "Voronoi", "TRUE")

MSE_vals <- rep(0, length(betas)*length(IW_types))

SE_vals <- rep(0, length(betas)*length(IW_types))

set.seed(1)
counter <- 1

num_boot_samples <- 100000

for(i in 1:length(betas)){
  res_list <- load_all_from_cluster(betas[i])
  
  cv_vals <- res_list$LOOCV
  
  ECRPS_vals <- res_list$ECRPS
  
  aggregated_vals <- aggregate_CV(cv_vals, Datasets = res_list$data)
  
  MSE_vals[counter] <- mean((aggregated_vals-ECRPS_vals)^2)
  
  boot_obj <- boot(data=aggregated_vals,
                 statistic = boot_statistic,
                 R= num_boot_samples,
                 ECRPS_vals = res_list$ECRPS)
  
  SE_vals[counter] <- sd(boot_obj$t)
  
  counter <- counter+1
  
  for(j in c(7:10, 12)){
    # Positions:
    # 7 - KMM
    # 8 - KLIEP
    # 9 - Vor
    # 10 - True
    # 11 - ECRPS
    # 12 - KMM (median)
    
    if(j==9){
      norm_IWs <- res_list[[j]]
      for(k in 1:ncol(res_list[[j]])){
        norm_IWs[, k] <- 1/norm_IWs[, k]
        norm_IWs[, k] <- norm_IWs[, k]/mean(norm_IWs[, k])
      }
      aggregated_vals <- aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs=norm_IWs, Datasets=res_list$data)  
    }
    
    else if( j==10){ #Normalizing true weights and voronoi to have mean 1
      norm_IWs <- res_list[[j]]
      for(k in 1:ncol(res_list[[j]])){
        norm_IWs[, k] <- norm_IWs[, k]/mean(norm_IWs[, k])
      }
      aggregated_vals <- aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs=norm_IWs, Datasets=res_list$data)   
    }
    else{
      aggregated_vals<-aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs =res_list[[j]], Datasets=res_list$data)   
    }
    
    MSE_vals[counter] <- mean((aggregated_vals-ECRPS_vals)^2)
    
    boot_obj <- boot(data=aggregated_vals,
                 statistic = boot_statistic,
                 R= num_boot_samples,
                 ECRPS_vals = res_list$ECRPS)
    
    SE_vals[counter] <- sd(boot_obj$t)
    
    counter <- counter+1
  }
}

formatted_MSE <- format(MSE_vals, scientific = TRUE, digits = 2)
formatted_SE <- format(SE_vals, scientific = TRUE, digits = 2)

# Create the data frame
table_data <- data.frame(
  `beta` = betas,
  `No IWs` = paste0("mc{", formatted_MSE[seq(1, length(MSE_vals), by = 6)], 
                    " (", formatted_SE[seq(1, length(SE_vals), by = 6)], ")}"),
  KMM = paste0("mc{",formatted_MSE[seq(2, length(MSE_vals), by = 6)], 
               " (", formatted_SE[seq(2, length(SE_vals), by = 6)], ")}"),
  
  KMM_med = paste0("mc{",formatted_MSE[seq(6, length(MSE_vals), by = 6)], 
               " (", formatted_SE[seq(6, length(SE_vals), by = 6)], ")}"),
  
  KLIEP = paste0("mc{",formatted_MSE[seq(3, length(MSE_vals), by = 6)], 
                 " (", formatted_SE[seq(3, length(SE_vals), by = 6)], ")}"),
  Voronoi = paste0("mc{",formatted_MSE[seq(4, length(MSE_vals), by = 6)], 
                   " (", formatted_SE[seq(4, length(SE_vals), by = 6)], ")}"),
  `True IWs` = paste0("mc{",formatted_MSE[seq(5, length(MSE_vals), by = 6)], 
                      " (", formatted_SE[seq(5, length(SE_vals), by = 6)], ")}")
)

# Generate LaTeX table
table_latex <- kable(
  table_data, 
  format = "latex", 
  caption = "MSE of the LOOCV estimator for different types of importance weights across different values for the LGCP parameter $\beta$. Text colored as \textcolor{mytextcolor}{this} denotes weighted LOOCV that attain the lowest MSE for a given $\beta$, while cells colored as \textcolor{mycellcolor}{this} denote combinations that give the lowest MSE across the different CV methods. Standard errors of the MSE estimates, obtained through bootstrapping, is given in the parantheses."
)

# Output LaTeX code
cat(table_latex)
```

```{r}
kable(table_data, format = "html", caption = "Efficacy of the LOOCV values estimator for different importance weights across different values for the LGCP parameter $\\beta$") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## 9-fold
```{r, asis=TRUE}
betas <- c(0, 0.5, 1, 1.5, 2)

IW_types <- IW_types <- c("None", "KMM", "KLIEP", "Voronoi", "TRUE",
                          "BLOCK", "KMM - median")

MSE_vals <- rep(0, length(betas)*length(IW_types))

SE_vals <- rep(0, length(betas)*length(IW_types))

counter <- 1
set.seed(1)

for(i in 1:length(betas)){
  res_list <- load_all_from_cluster(betas[i])
  
  cv_vals <- res_list$fold_9
  
  ECRPS_vals <- res_list$ECRPS
  
  aggregated_vals <- aggregate_CV(cv_vals, Datasets = res_list$data,
                                  method = "K", nFolds = 9)
  
  MSE_vals[counter] <- mean((aggregated_vals-ECRPS_vals)^2)
  
  boot_obj <- boot(data=aggregated_vals,
                 statistic = boot_statistic,
                 R= num_boot_samples,
                 ECRPS_vals = res_list$ECRPS)
  
  SE_vals[counter] <- sd(boot_obj$t)
  
  counter <- counter+1
  
  for(j in 7:12){

    
    if(j==9){
      norm_IWs <- res_list[[j]]
      for(k in 1:ncol(res_list[[j]])){
        norm_IWs[, k] <- 1/norm_IWs[, k]
        norm_IWs[, k] <- norm_IWs[, k]/mean(norm_IWs[, k])
      }
      aggregated_vals <- aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs=norm_IWs, Datasets=res_list$data)  
    }
    
    else if( j==10){ #Normalizing true weights and voronoi to have mean 1
      norm_IWs <- res_list[[j]]
      for(k in 1:ncol(res_list[[j]])){
        norm_IWs[, k] <- norm_IWs[, k]/mean(norm_IWs[, k])
      }
      aggregated_vals <- aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs=norm_IWs, Datasets=res_list$data)   
    }
    else if(j==11){
      aggregated_vals <- aggregate_CV(res_list$block_9, Datasets = res_list$data,
                                  method = "BLOCK", numBlocks = 9)
    }
    else{
      aggregated_vals<-aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs =res_list[[j]], Datasets=res_list$data, 
                          method = "K", nFolds = 9)   
    }
    
    
    MSE_vals[counter] <- mean((aggregated_vals-ECRPS_vals)^2)
  
    boot_obj <- boot(data=aggregated_vals,
                 statistic = boot_statistic,
                 R= num_boot_samples,
                 ECRPS_vals = res_list$ECRPS)
  
    SE_vals[counter] <- sd(boot_obj$t)
    
    counter <- counter+1
  }
}

formatted_MSE <- format(MSE_vals, scientific = TRUE, digits = 2)
formatted_SE <- format(SE_vals, scientific = TRUE, digits = 2)

# Create the data frame
table_data <- data.frame(
  `$beta$` = betas,
  `No IWs` = paste0("mc{", formatted_MSE[seq(1, length(MSE_vals), by = length(IW_types))], 
                    " (", formatted_SE[seq(1, length(SE_vals), by = length(IW_types))], ")}"),
  KMM = paste0("mc{", formatted_MSE[seq(2, length(MSE_vals), by = length(IW_types))], 
               " (", formatted_SE[seq(2, length(SE_vals), by = length(IW_types))], ")}"),
  KMM_med = paste0("mc{", formatted_MSE[seq(7, length(MSE_vals), by = length(IW_types))], 
               " (", formatted_SE[seq(7, length(SE_vals), by = length(IW_types))], ")}"),
  KLIEP = paste0("mc{", formatted_MSE[seq(3, length(MSE_vals), by = length(IW_types))], 
                 " (", formatted_SE[seq(3, length(SE_vals), by = length(IW_types))], ")}"),
  Voronoi = paste0("mc{", formatted_MSE[seq(4, length(MSE_vals), by = length(IW_types))], 
                   " (", formatted_SE[seq(4, length(SE_vals), by = length(IW_types))], ")}"),
  `True IWs` = paste0("mc{", formatted_MSE[seq(5, length(MSE_vals), by = length(IW_types))], 
                      " (", formatted_SE[seq(5, length(SE_vals), by = length(IW_types))], ")}"),
  `Block` = paste0("mc{", formatted_MSE[seq(6, length(MSE_vals), by = length(IW_types))], 
                      " (", formatted_SE[seq(6, length(SE_vals), by = length(IW_types))], ")}")
)

# Generate LaTeX table
table_latex <- kable(
  table_data, 
  format = "latex", 
  caption = "MSE of the 9-fold CV estimator for different types of importance weights across different values for the LGCP parameter $\beta$. Text colored as \textcolor{mytextcolor}{this} denotes weighted LOOCV that attain the lowest MSE for a given $\beta$, while cells colored as \textcolor{mycellcolor}{this} denote combinations that give the lowest MSE across the different CV methods. Standard errors of the MSE estimates, obtained through bootstrapping, is given in the parantheses."
)

# Output LaTeX code
cat(table_latex)
```

```{r}
# Generate LaTeX code using kable and kableExtra
kable(table_data, format = "html", caption = "Efficacy of the 9-fold CV estimator for different importance weights across different values for the LGCP parameter $\\beta$") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## 25-fold
```{r, asis=TRUE}
betas <- c(0, 0.5, 1, 1.5, 2)

IW_types <- IW_types <- c("None", "KMM", "KLIEP", "Voronoi", "TRUE",
                          "BLOCK", "KMM - median")

MSE_vals <- rep(0, length(betas)*length(IW_types))

SE_vals <- rep(0, length(betas)*length(IW_types))

counter <- 1

for(i in 1:length(betas)){
  res_list <- load_all_from_cluster(betas[i])
  
  cv_vals <- res_list$fold_25
  
  ECRPS_vals <- res_list$ECRPS
  
  aggregated_vals <- aggregate_CV(cv_vals, Datasets = res_list$data,
                                  method = "K", nFolds = 25)
  
  MSE_vals[counter] <- mean((aggregated_vals-ECRPS_vals)^2)
  
  boot_obj <- boot(data=aggregated_vals,
                 statistic = boot_statistic,
                 R= num_boot_samples,
                 ECRPS_vals = res_list$ECRPS)
  
  SE_vals[counter] <- sd(boot_obj$t)
  
  counter <- counter+1
  
  for(j in 7:12){
    
    if(j==9){
      norm_IWs <- res_list[[j]]
      for(k in 1:ncol(res_list[[j]])){
        norm_IWs[, k] <- 1/norm_IWs[, k]
        norm_IWs[, k] <- norm_IWs[, k]/mean(norm_IWs[, k])
      }
      aggregated_vals <- aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs=norm_IWs, Datasets=res_list$data)  
    }
    
    else if( j==10){ #Normalizing true weights and voronoi to have mean 1
      norm_IWs <- res_list[[j]]
      for(k in 1:ncol(res_list[[j]])){
        norm_IWs[, k] <- norm_IWs[, k]/mean(norm_IWs[, k])
      }
      aggregated_vals <- aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs=norm_IWs, Datasets=res_list$data)   
    }
    else if(j==11){
      aggregated_vals <- aggregate_CV(res_list$block_25, Datasets = res_list$data,
                                  method = "BLOCK", numBlocks = 25)
    }
    else{
      aggregated_vals<-aggregate_CV(cv_vals, IW_type = "SMTH",
                          IWs =res_list[[j]], Datasets=res_list$data, 
                          method = "K", nFolds = 25)   
    }
    
    
    MSE_vals[counter] <- mean((aggregated_vals-ECRPS_vals)^2)
  
    boot_obj <- boot(data=aggregated_vals,
                 statistic = boot_statistic,
                 R= num_boot_samples,
                 ECRPS_vals = res_list$ECRPS)
  
    SE_vals[counter] <- sd(boot_obj$t)
    
    counter <- counter+1
  }
}

formatted_MSE <- format(MSE_vals, scientific = TRUE, digits = 2)
formatted_SE <- format(SE_vals, scientific = TRUE, digits = 2)

# Create the data frame
table_data <- data.frame(
  `$beta$` = betas,
  `No IWs` = paste0("mc{", formatted_MSE[seq(1, length(MSE_vals), by = length(IW_types))], 
                    " (", formatted_SE[seq(1, length(SE_vals), by = length(IW_types))], ")}"),
  KMM = paste0("mc{", formatted_MSE[seq(2, length(MSE_vals), by = length(IW_types))], 
               " (", formatted_SE[seq(2, length(SE_vals), by = length(IW_types))], ")}"),
  KMM_med = paste0("mc{", formatted_MSE[seq(7, length(MSE_vals), by = length(IW_types))], 
               " (", formatted_SE[seq(7, length(SE_vals), by = length(IW_types))], ")}"),
  KLIEP = paste0("mc{", formatted_MSE[seq(3, length(MSE_vals), by = length(IW_types))], 
                 " (", formatted_SE[seq(3, length(SE_vals), by = length(IW_types))], ")}"),
  Voronoi = paste0("mc{", formatted_MSE[seq(4, length(MSE_vals), by = length(IW_types))], 
                   " (", formatted_SE[seq(4, length(SE_vals), by = length(IW_types))], ")}"),
  `True IWs` = paste0("mc{", formatted_MSE[seq(5, length(MSE_vals), by = length(IW_types))], 
                      " (", formatted_SE[seq(5, length(SE_vals), by = length(IW_types))], ")}"),
  `Block` = paste0("mc{", formatted_MSE[seq(6, length(MSE_vals), by = length(IW_types))], 
                      " (", formatted_SE[seq(6, length(SE_vals), by = length(IW_types))], ")}")
)

# Generate LaTeX table
table_latex <- kable(
  table_data, 
  format = "latex", 
  caption = "MSE of the 25-fold CV estimator for different types of importance weights across different values for the LGCP parameter $\beta$. Text colored as \textcolor{mytextcolor}{this} denotes weighted LOOCV that attain the lowest MSE for a given $\beta$, while cells colored as \textcolor{mycellcolor}{this} denote combinations that give the lowest MSE across the different CV methods. Standard errors of the MSE estimates, obtained through bootstrapping, is given in the parantheses."
)

# Output LaTeX code
cat(table_latex)
```
```{r}
kable(table_data, format = "html", caption = "Efficacy of the 25-fold CV estimator for different importance weights across different values for the LGCP parameter $\\beta$") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Delaunay Tessellation Figures

```{r}
calc_Voronoi_IWs <- function(data){
  dir <- deldir(data$x, data$y, rw=c(0,1,0,1))

  tiles <- tile.list(dir)
  areas <- rep(1, 2000)
  for(i in 1:2000){
    areas[i] <- tiles[[i]]$area
  }
  
  IWs <- areas/mean(areas)
  
  return(IWs)
}

crop_and_save <- function(figure, path, width=15, height=15){
  ggsave(path, plot=figure, units="cm", width=width, height=height)
  
  pdf_img <- image_read_pdf(path)

  # Trim whitespace from the edges
  cropped_pdf <- image_trim(pdf_img)
  
  # Save the cropped PDF
  image_write(cropped_pdf, path, format = "pdf")
}

library(ggforce)
library(deldir)
library(magick)

res_list <- load_all_from_cluster(0)

fig1 <- ggplot(res_list$data[[1]], aes(x=x, y=y))+
  coord_equal()+
  geom_voronoi_tile(aes(fill=log10(res_list$Vor[,1])), bound=c(0,1,0,1))+
  geom_voronoi_segment(bound=c(0,1,0,1),linewidth=0.001)+
  geom_point(size=0.1)+
  labs(x="", y="", fill="Voronoi IW")+
  scale_fill_gradient2(low="blue", high="red", mid="white",
                       breaks = c(-1, -0.5, 0, 0.5), # Breaks on the log scale
    #labels = c(0.1, 1, 3.16))+
    labels = c(expression(10^-1), expression(10^-0.5),
               1, expression(10^0.5)))+
  theme_dark()

crop_and_save(fig1, "Figures\\Voronoi IWs representative.pdf")

res_list <- load_all_from_cluster(2)

fig2 <- ggplot(res_list$data[[1]], aes(x=x, y=y))+
  coord_equal()+
  geom_voronoi_tile(aes(fill=log10(res_list$Vor[,1])), bound=c(0,1,0,1))+
  geom_voronoi_segment(bound=c(0,1,0,1), linewidth=0.001)+
  scale_fill_gradient2(low="blue", high="red", mid="white",
                       breaks = c(-2, -1, 0, 1), # Breaks on the log scale
    labels = c(expression(10^-2), expression(10^-1), expression(1), expression(10)))+
  geom_point(size=0.01)+
  labs(x="", y="", fill="Voronoi IW")+
  theme_dark()

crop_and_save(fig2, "Figures\\Voronoi IWs non-representative.pdf")
```

# KMM and KLIEP IWs

```{r}
res_list <- load_all_from_cluster(2)

fig3 <- ggplot(res_list$data[[1]], aes(x=x, y=y))+
  coord_equal()+
  geom_point(aes(color=log10(res_list$KMM[,1])))+
  labs(x="", y="", color="KMM IWs")+
   scale_color_gradient2(
    low = "blue", high = "red", mid = "white",
    breaks = c( 0, 1), # Breaks on the log scale
    labels = c( 1, 10))+
  theme_dark()

crop_and_save(fig3, "Figures\\KMM IWs non-rep.pdf")

fig4 <- ggplot(res_list$data[[1]], aes(x=x, y=y))+
  coord_equal()+
  geom_point(aes(color=log10(res_list$KLIEP[,1])))+
  labs(x="", y="", color="KLIEP IWs")+
  scale_color_gradient2(low="blue", high="red", mid="white",
                        breaks = c(-0.5, 0, 0.5, 1), # Breaks on the log scale
    labels = c(TeX("$10^{-0.5}$"), 1, expression(10^0.5), 10))+
  theme_dark()
crop_and_save(fig4, "Figures\\KLIEP IWs non-rep.pdf")
```

# Comparison of IWs' bias

```{r}
res_list <- load_all_from_cluster(0)

fig5 <- compare_IWs_violin(res_list)

crop_and_save(fig5, "Figures\\Representative IWs Bias.pdf")

res_list <- load_all_from_cluster(2)

fig6 <- compare_IWs_violin(res_list, 2)

crop_and_save(fig6, "Figures\\Non-Representative IWs Bias.pdf")
```

# Distribution of weights

```{r, eval=FALSE}
betas <- c(0, 0.5, 1, 1.5, 2)

lower_weights <- matrix(rep(0, 5*5), ncol=5, nrow=5)
colnames(lower_weights) <- c("KMM - tuned", "KLIEP", "Voronoi", "True", "KMM - median")

upper_weights <- matrix(rep(0, 5*5), ncol=5, nrow=5)

colnames(upper_weights) <- colnames(lower_weights)

for(i in 1:5){
  counter <- 1
  
  res_list <- load_all_from_cluster(betas[i])
  
  for(j in c(7:10, 12)){
    
    lower_weights[i, counter] <- min(c(res_list[[j]]))
      
    upper_weights[i, counter] <- max(c(res_list[[j]]))
    
    
    counter <- counter + 1
  }
}

plot_df <- data.frame(beta=betas)
lower_weights <- data.frame(lower_weights)
upper_weights <- data.frame(upper_weights)

bound_fig <- ggplot(data = plot_df, aes(x = betas)) +
  geom_segment( 
               aes(x = betas-0.1,
                   xend = betas-0.1,
                   y = lower_weights$KMM...tuned,
                   yend=upper_weights$KMM...tuned,
                   color="KMM - tuned"))+
 geom_segment( 
               aes(x = betas-0.05,
                   xend = betas-0.05,
                   y = lower_weights$KMM...median,
                   yend=upper_weights$KMM...median,
                   color="KMM - median"))+
  geom_segment( 
               aes(x = betas+0.05,
                   xend = betas+0.05,
                   y = lower_weights$KLIEP,
                   yend=upper_weights$KLIEP,
                   color="KLIEP"))+
  geom_segment( 
               aes(x = betas+0.1,
                   xend = betas+0.1,
                   y = lower_weights$Voronoi,
                   yend=upper_weights$Voronoi,
                   color="Voronoi"))+
  geom_segment( 
               aes(x = betas,
                   xend = betas,
                   y = lower_weights$True,
                   yend=upper_weights$True,
                   color="True"))+
  geom_point(aes(x=0, y=1, color="True"))+
  
  scale_y_continuous(trans='log10')+
  labs(x="Beta", y="Range of importance weights", colour="IW type")

crop_and_save(bound_fig, "Figures\\Range of IWs.pdf",width=20, height=10 )

crop_and_save(compare_IWs_violin(load_all_from_cluster(0), 0), "Figures\\Representative Bias of IWs.pdf",width=20, height=10)

crop_and_save(compare_IWs_violin(load_all_from_cluster(1), 1), "Figures\\Beta=1 Bias of IWs.pdf",width=20, height=10)

crop_and_save(compare_IWs_violin(load_all_from_cluster(2), 2), "Figures\\Non-Representative Bias of IWs.pdf",width=20, height=10)
```



